Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars

### 2014-10-21 drafts/cfp/draft.tex

\title{Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars}
\author{Eyal Dechter, Josh Rule, Josh Tenenbaum ADD AFFILIATION}
\date{}

\begin{document}
\vspace{-10cm}
\maketitle
\vspace{-6em}

{\small For humans, learning abstract concepts and learning language
  go hand in hand: we acquire abstract knowledge primarily through
  linguistic experience, and acquiring abstract concepts is a crucial
  step in learning the meanings of linguistic expressions. Number
  knowledge is a case in point: we largely acquire concepts such as
  seventy-three through linguistic means, and we can only know what
  the sentence ``Seventy-three is more than twice as big as
  thirty-one" means if we can grasp the meanings of its component
  number words. How do we make sense of this potential paradox? One
  approach is to estimate the distribution from which sentences are
  drawn, and, in doing so, infer the latent concepts and relationships
  that best explain those sentences. We present early work on a
  learning framework called Latent Predicate Networks (LPNs) which
  learns concepts by inferring the parameters of probabilistic
  context-sensitive grammars over sentences.  We show that for a small
  fragment of sentences expressing relationships between English
  number words, we can use hierarchical Bayesian inference to learn
  LPNs that can answer simple queries about previously unseen abstract
  concepts within this domain. These generalizations demonstrate LPNs'
  promise as a tool for learning and representing conceptual knowledge
  in language.}

@@

Though simple, the knowledge learned by LPNs in the simple number
domain we explore in this paper goes beyond the expressive capacity of
PCFGs and HMMs, and yet it avoids intractability by using a restricted
formalism. The human ability to learn abstract concepts must also rely
on such a compromise, and it remains to be seen to what extent LPNs
can model this ability.

@@

Many of the algorithms and formalisms used here were originally
developed for use in other closely related areas, including logic
programming and semantic parsing. Semantic parsing, in particular,
seems especially related to the challenge we face here of jointly
learning meaning and structure from
sentences~\cite{berant2013semantic, liang2013learning,
  kwiatkowski2010inducing}. Semantic parsing, however, tends to frame
this challenge slightly differently than we do here, by asking
how utterances can be mapped to an explicit internal logical
language. By contrast, we focus here on systems where meaning and
structure seem inseparable. Understanding how these two approaches
relate and inform one another is an interesting and open question.

>>>>

\title{Latent Predicate Networks: Concept Learning with Probabilistic Context-Sensitive Grammars}
\author{Eyal Dechter (edechter)}
\author{Joshua Rule (rule)}
\author{Joshua B. Tenenbaum (jbt)}
\affil{Department of Brain and Cognitive Sciences, MIT (mit.edu)}

\renewcommand\Authands{ and }
\date{}

\begin{document}
\vspace{-10cm}
\maketitle

\vspace{-6em}

{\small For humans, learning abstract concepts and learning language
  go hand in hand: we acquire abstract knowledge primarily through
  linguistic experience, and acquiring abstract concepts is a crucial
  step in learning the meanings of linguistic expressions. Number
  knowledge is a case in point: we largely acquire concepts such as
  seventy-three through linguistic means, and we can only know what
  the sentence ``Seventy-three is more than twice as big as
  thirty-one" means if we can grasp the meanings of its component
  number words. How do we begin to solve this problem? One approach is
  to estimate the distribution from which sentences are drawn, and, in
  doing so, infer the latent concepts and relationships that best
  explain those sentences. We present early work on a learning
  framework called Latent Predicate Networks (LPNs) which learns
  concepts by inferring the parameters of probabilistic
  context-sensitive grammars over sentences.  We show that for a small
  fragment of sentences expressing relationships between English
  number words, we can use hierarchical Bayesian inference to learn
  LPNs that can answer simple queries about previously unseen
  relationships within this domain. These generalizations demonstrate
  LPNs' promise as a tool for learning and representing conceptual
  knowledge in language.}

@@

Though simple, the knowledge learned by LPNs in the number
domain we explore in this paper goes beyond the expressive capacity of
PCFGs and HMMs, and yet it avoids intractability by using a restricted
formalism. The human ability to learn abstract concepts must also rely
on such a compromise, and it remains to be seen to what extent LPNs
can model this ability.

@@

Many of the algorithms and formalisms used here were originally
developed for use in other closely related areas, including logic
programming and semantic parsing. Semantic parsing, in particular,
seems especially related to the challenge we face here of jointly
learning meaning and structure from
sentences~\cite{berant2013semantic, liang2013learning,
  kwiatkowski2010inducing, poon2009unsupervised}. Semantic parsing,
however, tends to frame this challenge slightly differently than we do
here, namely, by asking how utterances can be mapped to an explicit
internal logical language. By contrast, we focus here on systems where
meaning and structure seem inseparable. Understanding how these two
approaches relate and inform one another is an interesting and open
question.
